Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2024-08-07 doc/manuscript/SI_ForCv40.Rmd
misc improvements in response to reviews

Manual review of records was the limiting step for data submission to EFDB. 
We prioritized review of
(1) records from the Forest Global Earth Observatory [ForestGEO, @anderson-teixeira_ctfsforestgeo_2015; @davies_forestgeo_2021],
(2) studies with confidence intervals recorded in ForC (because uncertainty estimates are important to the IPCC),
(3) original publications containing large numbers of EFDB-relevant records,
and (4) records from tropical regions.
The latter criteria was motivated by the fact that although tropical forest is the single most important biome for climate change mitigation [@griscom_natural_2017;@griscom_national_2020], ground-based data on tropical forest C cycling tends to be more scarce due to a variety of challenges [@anderson-teixeira_carbon_2021; @delima_making_2022], and tropical countries are more likely to apply Tier 1 methodology that bases forest C budgets on internationally defined IPCC default values [@romijn_assessing_2015].

>>>>

Manual review of records was the limiting step for data submission to EFDB. 
We prioritized review of
(1) records from the Forest Global Earth Observatory [ForestGEO, @anderson-teixeira_ctfsforestgeo_2015; @davies_forestgeo_2021], which are familiar to our team and generally high quality,
(2) studies with confidence intervals recorded in ForC (because uncertainty estimates are important to the IPCC),
(3) original publications containing large numbers of EFDB-relevant records,
and (4) records from tropical regions.
The latter criteria was motivated by the fact that although tropical forest is the single most important biome for climate change mitigation [@griscom_natural_2017;@griscom_national_2020], ground-based data on tropical forest C cycling tends to be more scarce due to a variety of challenges [@anderson-teixeira_carbon_2021; @delima_making_2022], and tropical countries are more likely to apply Tier 1 methodology that bases forest C budgets on internationally defined IPCC default values [@romijn_assessing_2015].
